---
title: "canHealthWaitR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{canHealthWaitR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)

# Make sure all chunks run from the package root directory
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

```{r}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::load_all()
```


## Overview

canHealthWaitR is an R package that provides tools for exploring Canadian
health care wait time data from Statistics Canada's Web Data Service (WDS).

The package focuses on curated tables related to specialist wait times and
health care access indicators.

### 1. Discovering curated tables

The package provides a small registry of curated Statistics Canada (WDS) tables.

```{r}
getwd()
list.files()
setwd("..")          # 从 vignettes 回到包根目录
getwd()
list.files()
```
